\Large \bf Cyclone: High Availability for Persistent Key Value Stores

### 2017-07-29 paper/paper.tex
Updates to paper.

The core network operation in replication is to receive a request from the
client at the leader replica and send that exact same request (as a log entry)
to all follower replicas. The leader therefore \emph{multicasts} a received
request packet to follower replicas, a problem well studied in the networking
community when building software packet switches. Software packet switches reach
impressive speeds of millions of packets forwarded per core [find refs], a
number far in excess of the few hundreds of packets we manage in
Figure~\ref{fig:problem}. We therefore proceed by approximating a software
packet switch for the networking component of Cyclone. However software packet
switching does not need to deal with failure - usually requiring only a simple
decision for each packet at the node. RAFT introduces significant
protocol level work for each forwarded packet a challenge that we need to deal
with to approach the desired software packet switching efficiency in the common
case.

>>>>

The core network operation in replication is to receive a request from the
client at the leader replica and send that exact same request (as a log entry)
to all follower replicas. The leader therefore \emph{multicasts} a received
request packet to follower replicas, a problem well studied in the networking
community when building software packet switches. Software packet switches reach
impressive speeds of millions of packets forwarded per second~\cite{dpdk_perf}, a
number far in excess of the few hundreds of packets we manage in
Figure~\ref{fig:problem}. We therefore proceed by approximating a software
packet switch for the networking component of Cyclone. However software packet
switching does not need to deal with failure - usually requiring only a simple
decision for each packet at the node. RAFT introduces significant
protocol level work for each forwarded packet a challenge that we need to deal
with to approach the desired software packet switching efficiency in the common
case.
